Back to Normal Transits for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-04-14 ms.tex
added kepler stuff, pca and river plot

>>>>

\section{Kepler Re-analysis}
We examine the 17 total quarters of Kepler data.
There is not detectable secondary eclipse at $\lesssim 50$ ppm, seen in Figure \ref{fig:secEclipse}. 
The constraint is even tighter assuming a circular orbit.

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.8\textwidth]{images/kepler/secondary_eclipse.pdf}
\caption{Secondary eclipse found by averaging the light curve from 17 quarters of Kepler data.}\label{fig:secEclipse}
\end{centering}
\end{figure*}

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/photometry_riverplot.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/pca_k1255.pdf}
\caption{Cleaned Kepler Long-cadence data and PCA analysis.}\label{fig:kepPCA}
\end{centering}
\end{figure*}
